---
title: "MockConjugation_RFU_GrowthCurve"
output: html_document
date: "2024-12-23"
---

```{r}
library(readxl)
library(tidyverse)
library(dplyr)
library(purrr)
```

##this code is for building a dataframe for Tc10 (all strains)

```{r}
Day0_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240527_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day0_Tc10_OD <- Day0_Tc10[-OD_rows_to_skip, ]
Day0_Tc10_RFU <- Day0_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day0_Tc10_RFU[8, 12]
reference_value <- Day0_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day0_Tc10_RFU_adjusted <- Day0_Tc10_RFU
Day0_Tc10_OD_adjusted <- Day0_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day0_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day0_Tc10_RFU_adjusted)) {
    Day0_Tc10_RFU_adjusted[i, j] <- Day0_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day0_Tc10_RFU_adjusted[i, j] < 0) {
      Day0_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day0_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day0_Tc10_OD_adjusted)) {
    Day0_Tc10_OD_adjusted[i, j] <- Day0_Tc10_OD_adjusted[i, j] - reference_value
    if (Day0_Tc10_OD_adjusted[i, j] < 0) {
      Day0_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

```{r}
Day1_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240528_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day1_Tc10_OD <- Day1_Tc10[-OD_rows_to_skip, ]
Day1_Tc10_RFU <- Day1_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day1_Tc10_RFU[8, 12]
reference_value <- Day1_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day1_Tc10_RFU_adjusted <- Day1_Tc10_RFU
Day1_Tc10_OD_adjusted <- Day1_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day1_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day1_Tc10_RFU_adjusted)) {
    Day1_Tc10_RFU_adjusted[i, j] <- Day1_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day1_Tc10_RFU_adjusted[i, j] < 0) {
      Day1_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day1_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day1_Tc10_OD_adjusted)) {
    Day1_Tc10_OD_adjusted[i, j] <- Day1_Tc10_OD_adjusted[i, j] - reference_value
    if (Day1_Tc10_OD_adjusted[i, j] < 0) {
      Day1_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

```{r}
Day2_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240529_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day2_Tc10_OD <- Day2_Tc10[-OD_rows_to_skip, ]
Day2_Tc10_RFU <- Day2_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day2_Tc10_RFU[8, 12]
reference_value <- Day2_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day2_Tc10_RFU_adjusted <- Day2_Tc10_RFU
Day2_Tc10_OD_adjusted <- Day2_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day2_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day2_Tc10_RFU_adjusted)) {
    Day2_Tc10_RFU_adjusted[i, j] <- Day2_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day2_Tc10_RFU_adjusted[i, j] < 0) {
      Day2_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day2_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day2_Tc10_OD_adjusted)) {
    Day2_Tc10_OD_adjusted[i, j] <- Day2_Tc10_OD_adjusted[i, j] - reference_value
    if (Day2_Tc10_OD_adjusted[i, j] < 0) {
      Day2_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

```{r}
Day3_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240530_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day3_Tc10_OD <- Day3_Tc10[-OD_rows_to_skip, ]
Day3_Tc10_RFU <- Day3_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day3_Tc10_RFU[8, 12]
reference_value <- Day3_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day3_Tc10_RFU_adjusted <- Day3_Tc10_RFU
Day3_Tc10_OD_adjusted <- Day3_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day3_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day3_Tc10_RFU_adjusted)) {
    Day3_Tc10_RFU_adjusted[i, j] <- Day3_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day3_Tc10_RFU_adjusted[i, j] < 0) {
      Day3_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day3_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day3_Tc10_OD_adjusted)) {
    Day3_Tc10_OD_adjusted[i, j] <- Day3_Tc10_OD_adjusted[i, j] - reference_value
    if (Day3_Tc10_OD_adjusted[i, j] < 0) {
      Day3_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

```{r}
Day4_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240531_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day4_Tc10_OD <- Day4_Tc10[-OD_rows_to_skip, ]
Day4_Tc10_RFU <- Day4_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day4_Tc10_RFU[8, 12]
reference_value <- Day4_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day4_Tc10_RFU_adjusted <- Day4_Tc10_RFU
Day4_Tc10_OD_adjusted <- Day4_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day4_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day4_Tc10_RFU_adjusted)) {
    Day4_Tc10_RFU_adjusted[i, j] <- Day4_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day4_Tc10_RFU_adjusted[i, j] < 0) {
      Day4_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day4_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day4_Tc10_OD_adjusted)) {
    Day4_Tc10_OD_adjusted[i, j] <- Day4_Tc10_OD_adjusted[i, j] - reference_value
    if (Day4_Tc10_OD_adjusted[i, j] < 0) {
      Day4_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

```{r}
Day5_Tc10 <- read_excel("C:/Users/Riley/OneDrive/Desktop/Second Mock Conjugation5-23-24/240601_RW_Tc10.xlsx", range = "C35:N51", n_max = Inf)
OD_rows_to_skip <- c(2,4,6,8,10,12,14,16)
RFU_rows_to_skip <- c(1,3,5,7,9,11,13,15,17)
Day5_Tc10_OD <- Day5_Tc10[-OD_rows_to_skip, ]
Day5_Tc10_RFU <- Day5_Tc10[-RFU_rows_to_skip, ]

# Specify the cell value you want to subtract
reference_value <- Day5_Tc10_RFU[8, 12]
reference_value <- Day5_Tc10_OD[8, 12]

# Create a copy of the original data frame
Day5_Tc10_RFU_adjusted <- Day5_Tc10_RFU
Day5_Tc10_OD_adjusted <- Day5_Tc10_OD

# Subtract the reference value from each cell in the data frame
for (i in 1:nrow(Day5_Tc10_RFU_adjusted)) {
  for (j in 1:ncol(Day5_Tc10_RFU_adjusted)) {
    Day5_Tc10_RFU_adjusted[i, j] <- Day5_Tc10_RFU_adjusted[i, j] - reference_value
    if (Day5_Tc10_RFU_adjusted[i, j] < 0) {
      Day5_Tc10_RFU_adjusted[i, j] <- 0
    }
  }
}

for (i in 1:nrow(Day5_Tc10_OD_adjusted)) {
  for (j in 1:ncol(Day5_Tc10_OD_adjusted)) {
    Day5_Tc10_OD_adjusted[i, j] <- Day5_Tc10_OD_adjusted[i, j] - reference_value
    if (Day5_Tc10_OD_adjusted[i, j] < 0) {
      Day5_Tc10_OD_adjusted[i, j] <- 0
    }
  }
}
```

##Extract the OD by Day for each strain based on the row and column position in the dataframe

```{r}
# Define the data frame RmP110_A_1to1_RFU_adjusted
RmP110_A_1to1_RFU <- data.frame(
  Cell = c("RmP110_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 1],
  Day1 = Day1_Tc10_RFU_adjusted[1, 1],
  Day2 = Day2_Tc10_RFU_adjusted[1, 1],
  Day3 = Day3_Tc10_RFU_adjusted[1, 1],
  Day4 = Day4_Tc10_RFU_adjusted[1, 1],
  Day5 = Day5_Tc10_RFU_adjusted[1, 1]
)
colnames(RmP110_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_B_1to1_RFU <- data.frame(
  Cell = c("RmP110_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 2],
  Day1 = Day1_Tc10_RFU_adjusted[1, 2],
  Day2 = Day2_Tc10_RFU_adjusted[1, 2],
  Day3 = Day3_Tc10_RFU_adjusted[1, 2],
  Day4 = Day4_Tc10_RFU_adjusted[1, 2],
  Day5 = Day5_Tc10_RFU_adjusted[1, 2]
)
colnames(RmP110_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_C_1to1_RFU <- data.frame(
  Cell = c("RmP110_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 3],
  Day1 = Day1_Tc10_RFU_adjusted[1, 3],
  Day2 = Day2_Tc10_RFU_adjusted[1, 3],
  Day3 = Day3_Tc10_RFU_adjusted[1, 3],
  Day4 = Day4_Tc10_RFU_adjusted[1, 3],
  Day5 = Day5_Tc10_RFU_adjusted[1, 3]
)
colnames(RmP110_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


RmP110_A_2to1_RFU <- data.frame(
  Cell = c("RmP110_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 4],
  Day1 = Day1_Tc10_RFU_adjusted[1, 4],
  Day2 = Day2_Tc10_RFU_adjusted[1, 4],
  Day3 = Day3_Tc10_RFU_adjusted[1, 4],
  Day4 = Day4_Tc10_RFU_adjusted[1, 4],
  Day5 = Day5_Tc10_RFU_adjusted[1, 4]
)
colnames(RmP110_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_B_2to1_RFU <- data.frame(
  Cell = c("RmP110_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 5],
  Day1 = Day1_Tc10_RFU_adjusted[1, 5],
  Day2 = Day2_Tc10_RFU_adjusted[1, 5],
  Day3 = Day3_Tc10_RFU_adjusted[1, 5],
  Day4 = Day4_Tc10_RFU_adjusted[1, 5],
  Day5 = Day5_Tc10_RFU_adjusted[1, 5]
)
colnames(RmP110_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_C_2to1_RFU <- data.frame(
  Cell = c("RmP110_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 6],
  Day1 = Day1_Tc10_RFU_adjusted[1, 6],
  Day2 = Day2_Tc10_RFU_adjusted[1, 6],
  Day3 = Day3_Tc10_RFU_adjusted[1, 6],
  Day4 = Day4_Tc10_RFU_adjusted[1, 6],
  Day5 = Day5_Tc10_RFU_adjusted[1, 6]
)
colnames(RmP110_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



RmP110_A_5to1_RFU <- data.frame(
  Cell = c("RmP110_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 7],
  Day1 = Day1_Tc10_RFU_adjusted[1, 7],
  Day2 = Day2_Tc10_RFU_adjusted[1, 7],
  Day3 = Day3_Tc10_RFU_adjusted[1, 7],
  Day4 = Day4_Tc10_RFU_adjusted[1, 7],
  Day5 = Day5_Tc10_RFU_adjusted[1, 7]
)
colnames(RmP110_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_B_5to1_RFU <- data.frame(
  Cell = c("RmP110_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 8],
  Day1 = Day1_Tc10_RFU_adjusted[1, 8],
  Day2 = Day2_Tc10_RFU_adjusted[1, 8],
  Day3 = Day3_Tc10_RFU_adjusted[1, 8],
  Day4 = Day4_Tc10_RFU_adjusted[1, 8],
  Day5 = Day5_Tc10_RFU_adjusted[1, 8]
)
colnames(RmP110_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

RmP110_C_5to1_RFU <- data.frame(
  Cell = c("RmP110_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[1, 9],
  Day1 = Day1_Tc10_RFU_adjusted[1, 9],
  Day2 = Day2_Tc10_RFU_adjusted[1, 9],
  Day3 = Day3_Tc10_RFU_adjusted[1, 9],
  Day4 = Day4_Tc10_RFU_adjusted[1, 9],
  Day5 = Day5_Tc10_RFU_adjusted[1, 9]
)
colnames(RmP110_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
USDA110_A_1to1_RFU <- data.frame(
  Cell = c("USDA110_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 1],
  Day1 = Day1_Tc10_RFU_adjusted[2, 1],
  Day2 = Day2_Tc10_RFU_adjusted[2, 1],
  Day3 = Day3_Tc10_RFU_adjusted[2, 1],
  Day4 = Day4_Tc10_RFU_adjusted[2, 1],
  Day5 = Day5_Tc10_RFU_adjusted[2, 1]
)
colnames(USDA110_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_B_1to1_RFU <- data.frame(
  Cell = c("USDA110_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 2],
  Day1 = Day1_Tc10_RFU_adjusted[2, 2],
  Day2 = Day2_Tc10_RFU_adjusted[2, 2],
  Day3 = Day3_Tc10_RFU_adjusted[2, 2],
  Day4 = Day4_Tc10_RFU_adjusted[2, 2],
  Day5 = Day5_Tc10_RFU_adjusted[2, 2]
)
colnames(USDA110_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_C_1to1_RFU <- data.frame(
  Cell = c("USDA110_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 3],
  Day1 = Day1_Tc10_RFU_adjusted[2, 3],
  Day2 = Day2_Tc10_RFU_adjusted[2, 3],
  Day3 = Day3_Tc10_RFU_adjusted[2, 3],
  Day4 = Day4_Tc10_RFU_adjusted[2, 3],
  Day5 = Day5_Tc10_RFU_adjusted[2, 3]
)
colnames(USDA110_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


USDA110_A_2to1_RFU <- data.frame(
  Cell = c("USDA110_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 4],
  Day1 = Day1_Tc10_RFU_adjusted[2, 4],
  Day2 = Day2_Tc10_RFU_adjusted[2, 4],
  Day3 = Day3_Tc10_RFU_adjusted[2, 4],
  Day4 = Day4_Tc10_RFU_adjusted[2, 4],
  Day5 = Day5_Tc10_RFU_adjusted[2, 4]
)
colnames(USDA110_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_B_2to1_RFU <- data.frame(
  Cell = c("USDA110_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 5],
  Day1 = Day1_Tc10_RFU_adjusted[2, 5],
  Day2 = Day2_Tc10_RFU_adjusted[2, 5],
  Day3 = Day3_Tc10_RFU_adjusted[2, 5],
  Day4 = Day4_Tc10_RFU_adjusted[2, 5],
  Day5 = Day5_Tc10_RFU_adjusted[2, 5]
)
colnames(USDA110_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_C_2to1_RFU <- data.frame(
  Cell = c("USDA110_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 6],
  Day1 = Day1_Tc10_RFU_adjusted[2, 6],
  Day2 = Day2_Tc10_RFU_adjusted[2, 6],
  Day3 = Day3_Tc10_RFU_adjusted[2, 6],
  Day4 = Day4_Tc10_RFU_adjusted[2, 6],
  Day5 = Day5_Tc10_RFU_adjusted[2, 6]
)
colnames(USDA110_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



USDA110_A_5to1_RFU <- data.frame(
  Cell = c("USDA110_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 7],
  Day1 = Day1_Tc10_RFU_adjusted[2, 7],
  Day2 = Day2_Tc10_RFU_adjusted[2, 7],
  Day3 = Day3_Tc10_RFU_adjusted[2, 7],
  Day4 = Day4_Tc10_RFU_adjusted[2, 7],
  Day5 = Day5_Tc10_RFU_adjusted[2, 7]
)
colnames(USDA110_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_B_5to1_RFU <- data.frame(
  Cell = c("USDA110_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 8],
  Day1 = Day1_Tc10_RFU_adjusted[2, 8],
  Day2 = Day2_Tc10_RFU_adjusted[2, 8],
  Day3 = Day3_Tc10_RFU_adjusted[2, 8],
  Day4 = Day4_Tc10_RFU_adjusted[2, 8],
  Day5 = Day5_Tc10_RFU_adjusted[2, 8]
)
colnames(USDA110_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

USDA110_C_5to1_RFU <- data.frame(
  Cell = c("USDA110_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[2, 9],
  Day1 = Day1_Tc10_RFU_adjusted[2, 9],
  Day2 = Day2_Tc10_RFU_adjusted[2, 9],
  Day3 = Day3_Tc10_RFU_adjusted[2, 9],
  Day4 = Day4_Tc10_RFU_adjusted[2, 9],
  Day5 = Day5_Tc10_RFU_adjusted[2, 9]
)
colnames(USDA110_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
R7A_A_1to1_RFU <- data.frame(
  Cell = c("R7A_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 1],
  Day1 = Day1_Tc10_RFU_adjusted[3, 1],
  Day2 = Day2_Tc10_RFU_adjusted[3, 1],
  Day3 = Day3_Tc10_RFU_adjusted[3, 1],
  Day4 = Day4_Tc10_RFU_adjusted[3, 1],
  Day5 = Day5_Tc10_RFU_adjusted[3, 1]
)
colnames(R7A_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_B_1to1_RFU <- data.frame(
  Cell = c("R7A_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 2],
  Day1 = Day1_Tc10_RFU_adjusted[3, 2],
  Day2 = Day2_Tc10_RFU_adjusted[3, 2],
  Day3 = Day3_Tc10_RFU_adjusted[3, 2],
  Day4 = Day4_Tc10_RFU_adjusted[3, 2],
  Day5 = Day5_Tc10_RFU_adjusted[3, 2]
)
colnames(R7A_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_C_1to1_RFU <- data.frame(
  Cell = c("R7A_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 3],
  Day1 = Day1_Tc10_RFU_adjusted[3, 3],
  Day2 = Day2_Tc10_RFU_adjusted[3, 3],
  Day3 = Day3_Tc10_RFU_adjusted[3, 3],
  Day4 = Day4_Tc10_RFU_adjusted[3, 3],
  Day5 = Day5_Tc10_RFU_adjusted[3, 3]
)
colnames(R7A_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


R7A_A_2to1_RFU <- data.frame(
  Cell = c("R7A_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 4],
  Day1 = Day1_Tc10_RFU_adjusted[3, 4],
  Day2 = Day2_Tc10_RFU_adjusted[3, 4],
  Day3 = Day3_Tc10_RFU_adjusted[3, 4],
  Day4 = Day4_Tc10_RFU_adjusted[3, 4],
  Day5 = Day5_Tc10_RFU_adjusted[3, 4]
)
colnames(R7A_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_B_2to1_RFU <- data.frame(
  Cell = c("R7A_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 5],
  Day1 = Day1_Tc10_RFU_adjusted[3, 5],
  Day2 = Day2_Tc10_RFU_adjusted[3, 5],
  Day3 = Day3_Tc10_RFU_adjusted[3, 5],
  Day4 = Day4_Tc10_RFU_adjusted[3, 5],
  Day5 = Day5_Tc10_RFU_adjusted[3, 5]
)
colnames(R7A_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_C_2to1_RFU <- data.frame(
  Cell = c("R7A_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 6],
  Day1 = Day1_Tc10_RFU_adjusted[3, 6],
  Day2 = Day2_Tc10_RFU_adjusted[3, 6],
  Day3 = Day3_Tc10_RFU_adjusted[3, 6],
  Day4 = Day4_Tc10_RFU_adjusted[3, 6],
  Day5 = Day5_Tc10_RFU_adjusted[3, 6]
)
colnames(R7A_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



R7A_A_5to1_RFU <- data.frame(
  Cell = c("R7A_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 7],
  Day1 = Day1_Tc10_RFU_adjusted[3, 7],
  Day2 = Day2_Tc10_RFU_adjusted[3, 7],
  Day3 = Day3_Tc10_RFU_adjusted[3, 7],
  Day4 = Day4_Tc10_RFU_adjusted[3, 7],
  Day5 = Day5_Tc10_RFU_adjusted[3, 7]
)
colnames(R7A_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_B_5to1_RFU <- data.frame(
  Cell = c("R7A_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 8],
  Day1 = Day1_Tc10_RFU_adjusted[3, 8],
  Day2 = Day2_Tc10_RFU_adjusted[3, 8],
  Day3 = Day3_Tc10_RFU_adjusted[3, 8],
  Day4 = Day4_Tc10_RFU_adjusted[3, 8],
  Day5 = Day5_Tc10_RFU_adjusted[3, 8]
)
colnames(R7A_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

R7A_C_5to1_RFU <- data.frame(
  Cell = c("R7A_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[3, 9],
  Day1 = Day1_Tc10_RFU_adjusted[3, 9],
  Day2 = Day2_Tc10_RFU_adjusted[3, 9],
  Day3 = Day3_Tc10_RFU_adjusted[3, 9],
  Day4 = Day4_Tc10_RFU_adjusted[3, 9],
  Day5 = Day5_Tc10_RFU_adjusted[3, 9]
)
colnames(R7A_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
Sp7_A_1to1_RFU <- data.frame(
  Cell = c("Sp7_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 1],
  Day1 = Day1_Tc10_RFU_adjusted[4, 1],
  Day2 = Day2_Tc10_RFU_adjusted[4, 1],
  Day3 = Day3_Tc10_RFU_adjusted[4, 1],
  Day4 = Day4_Tc10_RFU_adjusted[4, 1],
  Day5 = Day5_Tc10_RFU_adjusted[4, 1]
)
colnames(Sp7_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_B_1to1_RFU <- data.frame(
  Cell = c("Sp7_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 2],
  Day1 = Day1_Tc10_RFU_adjusted[4, 2],
  Day2 = Day2_Tc10_RFU_adjusted[4, 2],
  Day3 = Day3_Tc10_RFU_adjusted[4, 2],
  Day4 = Day4_Tc10_RFU_adjusted[4, 2],
  Day5 = Day5_Tc10_RFU_adjusted[4, 2]
)
colnames(Sp7_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_C_1to1_RFU <- data.frame(
  Cell = c("Sp7_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 3],
  Day1 = Day1_Tc10_RFU_adjusted[4, 3],
  Day2 = Day2_Tc10_RFU_adjusted[4, 3],
  Day3 = Day3_Tc10_RFU_adjusted[4, 3],
  Day4 = Day4_Tc10_RFU_adjusted[4, 3],
  Day5 = Day5_Tc10_RFU_adjusted[4, 3]
)
colnames(Sp7_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


Sp7_A_2to1_RFU <- data.frame(
  Cell = c("Sp7_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 4],
  Day1 = Day1_Tc10_RFU_adjusted[4, 4],
  Day2 = Day2_Tc10_RFU_adjusted[4, 4],
  Day3 = Day3_Tc10_RFU_adjusted[4, 4],
  Day4 = Day4_Tc10_RFU_adjusted[4, 4],
  Day5 = Day5_Tc10_RFU_adjusted[4, 4]
)
colnames(Sp7_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_B_2to1_RFU <- data.frame(
  Cell = c("Sp7_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 5],
  Day1 = Day1_Tc10_RFU_adjusted[4, 5],
  Day2 = Day2_Tc10_RFU_adjusted[4, 5],
  Day3 = Day3_Tc10_RFU_adjusted[4, 5],
  Day4 = Day4_Tc10_RFU_adjusted[4, 5],
  Day5 = Day5_Tc10_RFU_adjusted[4, 5]
)
colnames(Sp7_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_C_2to1_RFU <- data.frame(
  Cell = c("Sp7_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 6],
  Day1 = Day1_Tc10_RFU_adjusted[4, 6],
  Day2 = Day2_Tc10_RFU_adjusted[4, 6],
  Day3 = Day3_Tc10_RFU_adjusted[4, 6],
  Day4 = Day4_Tc10_RFU_adjusted[4, 6],
  Day5 = Day5_Tc10_RFU_adjusted[4, 6]
)
colnames(Sp7_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



Sp7_A_5to1_RFU <- data.frame(
  Cell = c("Sp7_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 7],
  Day1 = Day1_Tc10_RFU_adjusted[4, 7],
  Day2 = Day2_Tc10_RFU_adjusted[4, 7],
  Day3 = Day3_Tc10_RFU_adjusted[4, 7],
  Day4 = Day4_Tc10_RFU_adjusted[4, 7],
  Day5 = Day5_Tc10_RFU_adjusted[4, 7]
)
colnames(Sp7_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_B_5to1_RFU <- data.frame(
  Cell = c("Sp7_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 8],
  Day1 = Day1_Tc10_RFU_adjusted[4, 8],
  Day2 = Day2_Tc10_RFU_adjusted[4, 8],
  Day3 = Day3_Tc10_RFU_adjusted[4, 8],
  Day4 = Day4_Tc10_RFU_adjusted[4, 8],
  Day5 = Day5_Tc10_RFU_adjusted[4, 8]
)
colnames(Sp7_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

Sp7_C_5to1_RFU <- data.frame(
  Cell = c("Sp7_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[4, 9],
  Day1 = Day1_Tc10_RFU_adjusted[4, 9],
  Day2 = Day2_Tc10_RFU_adjusted[4, 9],
  Day3 = Day3_Tc10_RFU_adjusted[4, 9],
  Day4 = Day4_Tc10_RFU_adjusted[4, 9],
  Day5 = Day5_Tc10_RFU_adjusted[4, 9]
)
colnames(Sp7_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
IRBG74_A_1to1_RFU <- data.frame(
  Cell = c("IRBG74_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 1],
  Day1 = Day1_Tc10_RFU_adjusted[5, 1],
  Day2 = Day2_Tc10_RFU_adjusted[5, 1],
  Day3 = Day3_Tc10_RFU_adjusted[5, 1],
  Day4 = Day4_Tc10_RFU_adjusted[5, 1],
  Day5 = Day5_Tc10_RFU_adjusted[5, 1]
)
colnames(IRBG74_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_B_1to1_RFU <- data.frame(
  Cell = c("IRBG74_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 2],
  Day1 = Day1_Tc10_RFU_adjusted[5, 2],
  Day2 = Day2_Tc10_RFU_adjusted[5, 2],
  Day3 = Day3_Tc10_RFU_adjusted[5, 2],
  Day4 = Day4_Tc10_RFU_adjusted[5, 2],
  Day5 = Day5_Tc10_RFU_adjusted[5, 2]
)
colnames(IRBG74_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_C_1to1_RFU <- data.frame(
  Cell = c("IRBG74_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 3],
  Day1 = Day1_Tc10_RFU_adjusted[5, 3],
  Day2 = Day2_Tc10_RFU_adjusted[5, 3],
  Day3 = Day3_Tc10_RFU_adjusted[5, 3],
  Day4 = Day4_Tc10_RFU_adjusted[5, 3],
  Day5 = Day5_Tc10_RFU_adjusted[5, 3]
)
colnames(IRBG74_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


IRBG74_A_2to1_RFU <- data.frame(
  Cell = c("IRBG74_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 4],
  Day1 = Day1_Tc10_RFU_adjusted[5, 4],
  Day2 = Day2_Tc10_RFU_adjusted[5, 4],
  Day3 = Day3_Tc10_RFU_adjusted[5, 4],
  Day4 = Day4_Tc10_RFU_adjusted[5, 4],
  Day5 = Day5_Tc10_RFU_adjusted[5, 4]
)
colnames(IRBG74_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_B_2to1_RFU <- data.frame(
  Cell = c("IRBG74_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 5],
  Day1 = Day1_Tc10_RFU_adjusted[5, 5],
  Day2 = Day2_Tc10_RFU_adjusted[5, 5],
  Day3 = Day3_Tc10_RFU_adjusted[5, 5],
  Day4 = Day4_Tc10_RFU_adjusted[5, 5],
  Day5 = Day5_Tc10_RFU_adjusted[5, 5]
)
colnames(IRBG74_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_C_2to1_RFU <- data.frame(
  Cell = c("IRBG74_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 6],
  Day1 = Day1_Tc10_RFU_adjusted[5, 6],
  Day2 = Day2_Tc10_RFU_adjusted[5, 6],
  Day3 = Day3_Tc10_RFU_adjusted[5, 6],
  Day4 = Day4_Tc10_RFU_adjusted[5, 6],
  Day5 = Day5_Tc10_RFU_adjusted[5, 6]
)
colnames(IRBG74_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



IRBG74_A_5to1_RFU <- data.frame(
  Cell = c("IRBG74_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 7],
  Day1 = Day1_Tc10_RFU_adjusted[5, 7],
  Day2 = Day2_Tc10_RFU_adjusted[5, 7],
  Day3 = Day3_Tc10_RFU_adjusted[5, 7],
  Day4 = Day4_Tc10_RFU_adjusted[5, 7],
  Day5 = Day5_Tc10_RFU_adjusted[5, 7]
)
colnames(IRBG74_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_B_5to1_RFU <- data.frame(
  Cell = c("IRBG74_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 8],
  Day1 = Day1_Tc10_RFU_adjusted[5, 8],
  Day2 = Day2_Tc10_RFU_adjusted[5, 8],
  Day3 = Day3_Tc10_RFU_adjusted[5, 8],
  Day4 = Day4_Tc10_RFU_adjusted[5, 8],
  Day5 = Day5_Tc10_RFU_adjusted[5, 8]
)
colnames(IRBG74_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

IRBG74_C_5to1_RFU <- data.frame(
  Cell = c("IRBG74_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[5, 9],
  Day1 = Day1_Tc10_RFU_adjusted[5, 9],
  Day2 = Day2_Tc10_RFU_adjusted[5, 9],
  Day3 = Day3_Tc10_RFU_adjusted[5, 9],
  Day4 = Day4_Tc10_RFU_adjusted[5, 9],
  Day5 = Day5_Tc10_RFU_adjusted[5, 9]
)
colnames(IRBG74_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
M5A1_A_1to1_RFU <- data.frame(
  Cell = c("M5A1_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 1],
  Day1 = Day1_Tc10_RFU_adjusted[6, 1],
  Day2 = Day2_Tc10_RFU_adjusted[6, 1],
  Day3 = Day3_Tc10_RFU_adjusted[6, 1],
  Day4 = Day4_Tc10_RFU_adjusted[6, 1],
  Day5 = Day5_Tc10_RFU_adjusted[6, 1]
)
colnames(M5A1_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_B_1to1_RFU <- data.frame(
  Cell = c("M5A1_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 2],
  Day1 = Day1_Tc10_RFU_adjusted[6, 2],
  Day2 = Day2_Tc10_RFU_adjusted[6, 2],
  Day3 = Day3_Tc10_RFU_adjusted[6, 2],
  Day4 = Day4_Tc10_RFU_adjusted[6, 2],
  Day5 = Day5_Tc10_RFU_adjusted[6, 2]
)
colnames(M5A1_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_C_1to1_RFU <- data.frame(
  Cell = c("M5A1_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 3],
  Day1 = Day1_Tc10_RFU_adjusted[6, 3],
  Day2 = Day2_Tc10_RFU_adjusted[6, 3],
  Day3 = Day3_Tc10_RFU_adjusted[6, 3],
  Day4 = Day4_Tc10_RFU_adjusted[6, 3],
  Day5 = Day5_Tc10_RFU_adjusted[6, 3]
)
colnames(M5A1_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


M5A1_A_2to1_RFU <- data.frame(
  Cell = c("M5A1_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 4],
  Day1 = Day1_Tc10_RFU_adjusted[6, 4],
  Day2 = Day2_Tc10_RFU_adjusted[6, 4],
  Day3 = Day3_Tc10_RFU_adjusted[6, 4],
  Day4 = Day4_Tc10_RFU_adjusted[6, 4],
  Day5 = Day5_Tc10_RFU_adjusted[6, 4]
)
colnames(M5A1_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_B_2to1_RFU <- data.frame(
  Cell = c("M5A1_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 5],
  Day1 = Day1_Tc10_RFU_adjusted[6, 5],
  Day2 = Day2_Tc10_RFU_adjusted[6, 5],
  Day3 = Day3_Tc10_RFU_adjusted[6, 5],
  Day4 = Day4_Tc10_RFU_adjusted[6, 5],
  Day5 = Day5_Tc10_RFU_adjusted[6, 5]
)
colnames(M5A1_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_C_2to1_RFU <- data.frame(
  Cell = c("M5A1_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 6],
  Day1 = Day1_Tc10_RFU_adjusted[6, 6],
  Day2 = Day2_Tc10_RFU_adjusted[6, 6],
  Day3 = Day3_Tc10_RFU_adjusted[6, 6],
  Day4 = Day4_Tc10_RFU_adjusted[6, 6],
  Day5 = Day5_Tc10_RFU_adjusted[6, 6]
)
colnames(M5A1_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



M5A1_A_5to1_RFU <- data.frame(
  Cell = c("M5A1_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 7],
  Day1 = Day1_Tc10_RFU_adjusted[6, 7],
  Day2 = Day2_Tc10_RFU_adjusted[6, 7],
  Day3 = Day3_Tc10_RFU_adjusted[6, 7],
  Day4 = Day4_Tc10_RFU_adjusted[6, 7],
  Day5 = Day5_Tc10_RFU_adjusted[6, 7]
)
colnames(M5A1_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_B_5to1_RFU <- data.frame(
  Cell = c("M5A1_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 8],
  Day1 = Day1_Tc10_RFU_adjusted[6, 8],
  Day2 = Day2_Tc10_RFU_adjusted[6, 8],
  Day3 = Day3_Tc10_RFU_adjusted[6, 8],
  Day4 = Day4_Tc10_RFU_adjusted[6, 8],
  Day5 = Day5_Tc10_RFU_adjusted[6, 8]
)
colnames(M5A1_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

M5A1_C_5to1_RFU <- data.frame(
  Cell = c("M5A1_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[6, 9],
  Day1 = Day1_Tc10_RFU_adjusted[6, 9],
  Day2 = Day2_Tc10_RFU_adjusted[6, 9],
  Day3 = Day3_Tc10_RFU_adjusted[6, 9],
  Day4 = Day4_Tc10_RFU_adjusted[6, 9],
  Day5 = Day5_Tc10_RFU_adjusted[6, 9]
)
colnames(M5A1_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

##Extract the RFU by Day for each strain based on the row and column position in the dataframe

```{r}
ORS571_A_1to1_RFU <- data.frame(
  Cell = c("ORS571_A_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 1],
  Day1 = Day1_Tc10_RFU_adjusted[7, 1],
  Day2 = Day2_Tc10_RFU_adjusted[7, 1],
  Day3 = Day3_Tc10_RFU_adjusted[7, 1],
  Day4 = Day4_Tc10_RFU_adjusted[7, 1],
  Day5 = Day5_Tc10_RFU_adjusted[7, 1]
)
colnames(ORS571_A_1to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_B_1to1_RFU <- data.frame(
  Cell = c("ORS571_B_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 2],
  Day1 = Day1_Tc10_RFU_adjusted[7, 2],
  Day2 = Day2_Tc10_RFU_adjusted[7, 2],
  Day3 = Day3_Tc10_RFU_adjusted[7, 2],
  Day4 = Day4_Tc10_RFU_adjusted[7, 2],
  Day5 = Day5_Tc10_RFU_adjusted[7, 2]
)
colnames(ORS571_B_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_C_1to1_RFU <- data.frame(
  Cell = c("ORS571_C_1to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 3],
  Day1 = Day1_Tc10_RFU_adjusted[7, 3],
  Day2 = Day2_Tc10_RFU_adjusted[7, 3],
  Day3 = Day3_Tc10_RFU_adjusted[7, 3],
  Day4 = Day4_Tc10_RFU_adjusted[7, 3],
  Day5 = Day5_Tc10_RFU_adjusted[7, 3]
)
colnames(ORS571_C_1to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")


ORS571_A_2to1_RFU <- data.frame(
  Cell = c("ORS571_A_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 4],
  Day1 = Day1_Tc10_RFU_adjusted[7, 4],
  Day2 = Day2_Tc10_RFU_adjusted[7, 4],
  Day3 = Day3_Tc10_RFU_adjusted[7, 4],
  Day4 = Day4_Tc10_RFU_adjusted[7, 4],
  Day5 = Day5_Tc10_RFU_adjusted[7, 4]
)
colnames(ORS571_A_2to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_B_2to1_RFU <- data.frame(
  Cell = c("ORS571_B_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 5],
  Day1 = Day1_Tc10_RFU_adjusted[7, 5],
  Day2 = Day2_Tc10_RFU_adjusted[7, 5],
  Day3 = Day3_Tc10_RFU_adjusted[7, 5],
  Day4 = Day4_Tc10_RFU_adjusted[7, 5],
  Day5 = Day5_Tc10_RFU_adjusted[7, 5]
)
colnames(ORS571_B_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_C_2to1_RFU <- data.frame(
  Cell = c("ORS571_C_2to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 6],
  Day1 = Day1_Tc10_RFU_adjusted[7, 6],
  Day2 = Day2_Tc10_RFU_adjusted[7, 6],
  Day3 = Day3_Tc10_RFU_adjusted[7, 6],
  Day4 = Day4_Tc10_RFU_adjusted[7, 6],
  Day5 = Day5_Tc10_RFU_adjusted[7, 6]
)
colnames(ORS571_C_2to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")



ORS571_A_5to1_RFU <- data.frame(
  Cell = c("ORS571_A_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 7],
  Day1 = Day1_Tc10_RFU_adjusted[7, 7],
  Day2 = Day2_Tc10_RFU_adjusted[7, 7],
  Day3 = Day3_Tc10_RFU_adjusted[7, 7],
  Day4 = Day4_Tc10_RFU_adjusted[7, 7],
  Day5 = Day5_Tc10_RFU_adjusted[7, 7]
)
colnames(ORS571_A_5to1_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_B_5to1_RFU <- data.frame(
  Cell = c("ORS571_B_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 8],
  Day1 = Day1_Tc10_RFU_adjusted[7, 8],
  Day2 = Day2_Tc10_RFU_adjusted[7, 8],
  Day3 = Day3_Tc10_RFU_adjusted[7, 8],
  Day4 = Day4_Tc10_RFU_adjusted[7, 8],
  Day5 = Day5_Tc10_RFU_adjusted[7, 8]
)
colnames(ORS571_B_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

ORS571_C_5to1_RFU <- data.frame(
  Cell = c("ORS571_C_5to1"),
  Day0 = Day0_Tc10_RFU_adjusted[7, 9],
  Day1 = Day1_Tc10_RFU_adjusted[7, 9],
  Day2 = Day2_Tc10_RFU_adjusted[7, 9],
  Day3 = Day3_Tc10_RFU_adjusted[7, 9],
  Day4 = Day4_Tc10_RFU_adjusted[7, 9],
  Day5 = Day5_Tc10_RFU_adjusted[7, 9]
)
colnames(ORS571_C_5to1_RFU) <- c("Name", "Day 0", "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

#donor control

```{r}
Donor_Ctrl_NA_RFU <- data.frame(
  Cell = c("Donor_Ctrl_NA"),
  Day0 = Day1_Tc10_RFU_adjusted[1, 11],
  Day1 = Day1_Tc10_RFU_adjusted[1, 11],
  Day2 = Day2_Tc10_RFU_adjusted[1, 11],
  Day3 = Day3_Tc10_RFU_adjusted[1, 11],
  Day4 = Day4_Tc10_RFU_adjusted[1, 11],
  Day5 = Day5_Tc10_RFU_adjusted[1, 11]
)
colnames(Donor_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")

```

#recipient control

```{r}
RmP110Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("RmP110Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 1],
  Day1 = Day1_Tc10_RFU_adjusted[8, 1],
  Day2 = Day2_Tc10_RFU_adjusted[8, 1],
  Day3 = Day3_Tc10_RFU_adjusted[8, 1],
  Day4 = Day4_Tc10_RFU_adjusted[8, 1],
  Day5 = Day5_Tc10_RFU_adjusted[8, 1]
)
colnames(RmP110Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
USDA110Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("USDA110Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 2],
  Day1 = Day1_Tc10_RFU_adjusted[8, 2],
  Day2 = Day2_Tc10_RFU_adjusted[8, 2],
  Day3 = Day3_Tc10_RFU_adjusted[8, 2],
  Day4 = Day4_Tc10_RFU_adjusted[8, 2],
  Day5 = Day5_Tc10_RFU_adjusted[8, 2]
)
colnames(USDA110Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
R7ARecipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("R7ARecipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 3],
  Day1 = Day1_Tc10_RFU_adjusted[8, 3],
  Day2 = Day2_Tc10_RFU_adjusted[8, 3],
  Day3 = Day3_Tc10_RFU_adjusted[8, 3],
  Day4 = Day4_Tc10_RFU_adjusted[8, 3],
  Day5 = Day5_Tc10_RFU_adjusted[8, 3]
)
colnames(R7ARecipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
Sp7Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("Sp7Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 4],
  Day1 = Day1_Tc10_RFU_adjusted[8, 4],
  Day2 = Day2_Tc10_RFU_adjusted[8, 4],
  Day3 = Day3_Tc10_RFU_adjusted[8, 4],
  Day4 = Day4_Tc10_RFU_adjusted[8, 4],
  Day5 = Day5_Tc10_RFU_adjusted[8, 4]
)
colnames(Sp7Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
IRBG74Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("IRBG74Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 5],
  Day1 = Day1_Tc10_RFU_adjusted[8, 5],
  Day2 = Day2_Tc10_RFU_adjusted[8, 5],
  Day3 = Day3_Tc10_RFU_adjusted[8, 5],
  Day4 = Day4_Tc10_RFU_adjusted[8, 5],
  Day5 = Day5_Tc10_RFU_adjusted[8, 5]
)
colnames(IRBG74Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
M5A1Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("M5A1Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 6],
  Day1 = Day1_Tc10_RFU_adjusted[8, 6],
  Day2 = Day2_Tc10_RFU_adjusted[8, 6],
  Day3 = Day3_Tc10_RFU_adjusted[8, 6],
  Day4 = Day4_Tc10_RFU_adjusted[8, 6],
  Day5 = Day5_Tc10_RFU_adjusted[8, 6]
)
colnames(M5A1Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#recipient control

```{r}
ORS571Recipient_Ctrl_NA_RFU <- data.frame(
  Cell = c("ORS571Recipient_Ctrl_NA"),
  Day0 = Day0_Tc10_RFU_adjusted[8, 7],
  Day1 = Day1_Tc10_RFU_adjusted[8, 7],
  Day2 = Day2_Tc10_RFU_adjusted[8, 7],
  Day3 = Day3_Tc10_RFU_adjusted[8, 7],
  Day4 = Day4_Tc10_RFU_adjusted[8, 7],
  Day5 = Day5_Tc10_RFU_adjusted[8, 7]
)
colnames(ORS571Recipient_Ctrl_NA_RFU) <- c("Name", "Day 0",  "Day 1", "Day 2", "Day 3", "Day 4", "Day 5")
```

#Combine dataframes from samples/replicates and adjust for plotting

```{r}
Final_Tc10_RFU <- combined_df <- bind_rows(RmP110_A_1to1_RFU, RmP110_B_1to1_RFU, RmP110_C_1to1_RFU, RmP110_A_2to1_RFU, RmP110_B_2to1_RFU, RmP110_C_2to1_RFU, RmP110_A_5to1_RFU, RmP110_B_5to1_RFU, RmP110_C_5to1_RFU, USDA110_A_1to1_RFU, USDA110_B_1to1_RFU, USDA110_C_1to1_RFU, USDA110_A_2to1_RFU, USDA110_B_2to1_RFU, USDA110_C_2to1_RFU, USDA110_A_5to1_RFU, USDA110_B_5to1_RFU, USDA110_C_5to1_RFU, R7A_A_1to1_RFU, R7A_B_1to1_RFU, R7A_C_1to1_RFU, R7A_A_2to1_RFU, R7A_B_2to1_RFU, R7A_C_2to1_RFU, R7A_A_5to1_RFU, R7A_B_5to1_RFU, R7A_C_5to1_RFU,Sp7_A_1to1_RFU, Sp7_B_1to1_RFU, Sp7_C_1to1_RFU, Sp7_A_2to1_RFU, Sp7_B_2to1_RFU, Sp7_C_2to1_RFU, Sp7_A_5to1_RFU, Sp7_B_5to1_RFU, Sp7_C_5to1_RFU, IRBG74_A_1to1_RFU, IRBG74_B_1to1_RFU, IRBG74_C_1to1_RFU, IRBG74_A_2to1_RFU, IRBG74_B_2to1_RFU, IRBG74_C_2to1_RFU, IRBG74_A_5to1_RFU, IRBG74_B_5to1_RFU, IRBG74_C_5to1_RFU, M5A1_A_1to1_RFU, M5A1_B_1to1_RFU, M5A1_C_1to1_RFU, M5A1_A_2to1_RFU, M5A1_B_2to1_RFU, M5A1_C_2to1_RFU, M5A1_A_5to1_RFU, M5A1_B_5to1_RFU, M5A1_C_5to1_RFU, ORS571_A_1to1_RFU, ORS571_B_1to1_RFU, ORS571_C_1to1_RFU, ORS571_A_2to1_RFU, ORS571_B_2to1_RFU, ORS571_C_2to1_RFU, ORS571_A_5to1_RFU, ORS571_B_5to1_RFU, ORS571_C_5to1_RFU, Donor_Ctrl_NA_RFU, RmP110Recipient_Ctrl_NA_RFU, USDA110Recipient_Ctrl_NA_RFU, R7ARecipient_Ctrl_NA_RFU, Sp7Recipient_Ctrl_NA_RFU, IRBG74Recipient_Ctrl_NA_RFU, M5A1Recipient_Ctrl_NA_RFU, ORS571Recipient_Ctrl_NA_RFU, .id = "ID")

Final_Tc10_RFU <- separate(Final_Tc10_RFU, Name, into = c("Strain", "Replicate", "Ratio"), sep = "_")


```

Save the final table as excel

```{r}
write_excel_csv(Final_Tc10_RFU, "240813_RFU.xlsx")

```

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

# Load the data
file_name <- "C:/Users/Riley/OneDrive/Desktop/R_Studio/Scripts/240813_RFU.xlsx"
Final_Tc10_RFU <- read_excel(file_name, sheet = 1)

# Reshape the data
Final_Tc10_RFU_long <- Final_Tc10_RFU %>%
  pivot_longer(cols = starts_with("Day"),
               names_to = "Day",
               values_to = "Value")

# Calculate mean and standard deviation of replicates for each day
Final_Tc10_RFU_summary <- Final_Tc10_RFU_long %>%
  group_by(Strain, Ratio, Day) %>%
  summarize(mean_value = mean(Value),
            sd_value = sd(Value),
            .groups = 'drop')
```

```{r}
write_excel_csv(Final_Tc10_RFU_summary, "240813_RFU.xlsx")
```

setwd("C:/Users/Riley/OneDrive/Desktop/Growth Curve Analysis/")

```{r}
# Set output folder and file name
output_folder <- "C:/Users/Riley/OneDrive/Desktop/Growth Curve Analysis"
file_name <- "rfu_growth_curve.png"
file_path <- file.path(output_folder, file_name)

# Read the CSV file
csv_file <- "C:/Users/Riley/OneDrive/Desktop/Mock_RFU_Growth.csv"
d <- read.csv(csv_file, header = TRUE, sep = ",", stringsAsFactors = FALSE)

# Function to create growth curves
create_growth_curves <- function(data, output_path) {
  # Define y-axis limits and labels
  y_limits <- c(0, 200000)
  y_labels <- seq(0, 2, by = 0.5)
  
  # Create a PNG file to save all plots on one page with a transparent background
  png(output_path, width = 2000, height = 2000, bg = "transparent")
  
  # Set up the plotting area to have multiple plots on one page
  par(mfrow = c(6, 6), mar = c(4, 4, 2, 1), oma = c(1, 1, 1, 1), mgp = c(3, 1, 0))  # Adjust mfrow to fit all plots on one page
  
  for (col in colnames(data)[-1]) {
    if (is.numeric(data[[col]])) {
      # Identify the columns for the data and error values
      growth_col <- col
      error_col <- paste0(growth_col, "_SD")
      
      # Check if the error column exists
      if (!error_col %in% colnames(data)) {
        print(paste("Error column", error_col, "not found in data. Available columns:", paste(colnames(data), collapse = ", ")))
        next  # Skip to the next column
      }
      
      # Create plot
      plot(data$Time, data[[growth_col]], type = "o", col = "magenta", pch = 16, lwd = 3,
           ylim = y_limits,
           main = col, cex.main = 2,  # Larger main title
           ylab = "RFU", cex.lab = 1.5,  # Larger axis labels
           xlab = "Day", cex.axis = 1.5,  # Larger axis text
           yaxt = "n")
      axis(2, at = y_labels, labels = y_labels / 1000, cex.axis = 1.5)
      
      # Add error bars
      arrows(data$Time, data[[growth_col]] - data[[error_col]], data$Time, data[[growth_col]] + data[[error_col]],
             angle = 90, code = 3, length = 0.1, col = "magenta")
    }
  }
  
  # Close the PNG device
  dev.off()
  
  print(paste("All growth curves with error bars saved to", output_path))
}

# Call the function
create_growth_curves(d, file_path)
```





