---
title: "Plasmid_ID_Cleanup"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

This is a script for taking input data from plasmid_id python script used to process individual nodules in wells and produce output data regarding the frequency of plasmid_id occurence in nodules and number of mixed nodules.

```{r}
library(tidyverse)
library(dplyr)
```

Imports data for processing. 
*****change path to the input data.

```{r}
input_data <- read.csv("C:/Users/Riley/OneDrive/Desktop/240528_PlasmidID_analysis/MasterScripts_240528/R_Studio/240528_Analysis/Gm50_3_RW_Clean.csv") 
```

removes all values that did not detect forward or reverse barcode or plasmid ID (presumably due to sequencing errors)

```{r}
clean_data <-filter(input_data, fw_name != "none", rev_name != "none", pl_name != "none")

clean_data2 <-unite(clean_data, col="well", c("fw_name", "rev_name"), sep="_")

clean_data3 <- subset(clean_data2, select = -c(mean))
```

changes table configuration

```{r}
wider_data <- pivot_wider(clean_data3, names_from = pl_name, values_from = count)
```

sets the wells to rows

```{r}
wider_data2 <- column_to_rownames(wider_data, var = "well")
```

adds a column with the sum of for each well

```{r}
wider_data3 <- wider_data2 %>% replace(is.na(.), 0)%>%
  mutate(wider_data2, sum = rowSums(.))
```

moves the well label to row title

```{r}
wider_data4 <- rownames_to_column(wider_data3, var = "well")
```

changes the table composition to allow calculation of relative abundance

```{r}
longer_data <- wider_data4 %>%
  pivot_longer(cols=starts_with("rbc"), 
               names_to = "id_name",
               values_to = "id",
               values_drop_na = TRUE
  )
```